Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-07-01 paper/main.tex
revision of Methods until preprocessing

% what we did data source
In this study, we analyze data of three publicly available datasets from the
same set of 14 participants as part of the studyforrest data set
(\href{http://www.studyforrest.org}{studyforrest.org};
\citep{hanke2014audiomovie, hanke2016simultaneous}).
% PPA + movie + audio-description
We annotated cuts in the movie ``Forrest Gump'', and words spoken by an
additional narrator in the movie's audio-description (i.e. the movie's
audio-only variant) to exploratorily investigate how the parahippocampal gyrus
behaves during lifelike stimulation.
% model-driven analysis
In conformity to the analyses performed in the reviewed studies,  we also
employed a standard multi-level, voxel-wise general linear model
(GLM).\todo{why? in order to\dots}
% focus on audio-description
Encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus
on the audio-description as a naturalistic, auditory-only paradigm free from any task to localize a ``visual area'' in individual study participants.
% comparison to dedicated localizer
Finally, we compare our results to results of a dedicated visual localizer
experiment done with the same 14 participants \citep{sengupta2016extension}.

@@

% intro
We used data from three publicly available datasets, all being part of the
studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org})
which has already been used by other research groups for independent research
questions.
% used studies
\todo{this is just loveless listing so far but it's 'complete'}
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration}.
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}, a dataset already used by
\citep{ben2018hippocampal}.
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study) \citep{sengupta2016extension}, a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications \citep{hanke2014audiomovie, hanke2016simultaneous,
sengupta2016extension}. Following is a brief summary of most important aspects.

\subsection{Participants}

\todo[inline]{inner join von AO \& AV: N=14; AO: N=19; Exklusion von VP10 kommt
unter ``Data''}
% AO study
In the AO study, 19 German native speakers (all right-handed, age 21–38 years,
mean age 26.6 years, 12 male) listened to the German audio-description
\citep{ForrestGumpGermanAD} of the movie ``Forrest Gump''
\citep{ForrestGumpMovie} as an additional audio track for visually impaired
listeners on Swiss public television.
% AV study
In the AV study, 15 participants (21–39 years, mean age 29.4, six female) of the
prior AO study watched the audio-visual movie with dubbed German audio track
\citep{ForrestGumpDVD}.
% VIS study
In the VIS study, the same 15 participants took part in a six-category
block-design visual localizer.
% participants' health
All participants reported to have normal hearing, normal or corrected-to-normal
vision, and no known history of neurological disorders.
% compensation, consent and shit
In all studies, participants received monetary compensation and gave written
informed consent for their participation and for public sharing of obtained
data in anonymized form. The studies had prior approval by the Ethics Committee
of Otto-von-Guericke University of Magdeburg, Germany.

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned
audio-description (i.e. the audio-only variant of the movie) that was broadcast
as an additional audio track for visually impaired listeners on Swiss public
television \citep{ForrestGumpGermanAD}.
% AO vs. AV: differences
The plot of the movie is already carried by an off-screen voice of the main
character Forrest Gump. In the largely identical audio-description, an
additional male describes essential aspects of the visual scenery when there is
no off-screen voice, dialog, or other relevant auditory content.

@@

% VIS study picture categories
All stimuli for the VIS study were used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (matched in
luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
categories: human faces, human bodies without heads, small objects, houses and
outdoor scenes comprising of nature and street scenes, and phase scrambled
images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.

@@

% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted location \citep{haeusler2016cutanno}.
% AO anno
For the analysis of the AO data, we extended another publicly available
annotation of speech \citep{haeusler2020speechanno}. We manually annotated words
spoken by the audio-description's narrator:
% annotation procedure
Two persons performed a categorization of nouns embedded in sentences spoken by
the narrator to describe the movie's missing visual content.

\todo[inline]{WARUM WAS WIE annotiert wurde; warum Kategorien so gewählt?}

% categories Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der
% Zeit.
The nouns were categorized by the clue they provide about the cinematographic
scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent
persons (female, female name; male, male name, person), a person's appearance
(face, head; body, bodypart), and a scene's inherent objects (object,
furniture). See Table \ref{tab:descr-nouns-counts} for a complete overview of
all cateogries [+++rules, counts, examples].
% procedure
A preliminary annotation was performed by one person according to the rules (see
Table \ref{tab:descr-nouns-rules}). Minor corrections due to incorrectly applied
rules were by the author.

@@

% rules Tabelle für descriptiven nouns
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-description's narrator:
    cateogries, annotation rules and examples (given in English).}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & moveable objects insides and outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundarie & telephone, car \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & recurring setting & at the ``bus stop'' \tabularnewline
++ & nouns, adverbial adjectives and adverbs & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

@@

% counts Tabelle für descriptiven nouns
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-descriptions narrator:
        counts for the whole audio-only stimulus and its eight segments used
        during fMRI scanning.}
\label{tab:descr-nouns-counts}
\begin{tabular}{llllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
body & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline
bodypart &  \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline
face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline
female & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline
females & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline
fname & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline
furniture & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline
geo & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline
geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline
head & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline
male & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline
males & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline
mname & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline
object & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline
objects & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline
persons & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline

@@

\subsection{Procedure}
% questionnaire
In all three studies, participants filled out a questionnaire on their basic
demographic information (and familiarity with the audio-description or movie).
% AO & AV: instructions
Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions respectively. Between sessions, participants
left the scanner for a break with a flexible duration. Structural images were
obtained during the first study on a day different from the fMRI session.
% VIS: presentation & instructions
In the VIS study, participants were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run, while they also
performed a one-back matching task to keep them attentive.

@@

% AV & VIS
In the AV and VIS study, visual instructions and stimuli were presented on a
rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with
EXT-DVI-FM1000)].
% screen size
The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p}
resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with
\unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$
21.2]{cm}.
% angle of view: AV
In the AV study, this corresponded to \unit[23.75 $\times$ 13.5] or \unit[23.75
$times$ 10.25]{cm} when considering only the movie content and excluding the
horizontal gray bars.
% angle of view: VIS
In the VIS study, stimulus images were displayed at a size of approximately
\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.

\todo[inline]{Ist richtig, dass auditory stimulation in beiden Experimenten die
gleiche war?}

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices & FOV
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a 10 percent inter-slice gap were recorded in ascending order.
Slices were oriented to include the ventral portions of frontal and order.
Slices were oriented to include the ventral the ventral portions of frontal and
occipital cortex while minimizing intersection with the eyeballs.  The field of
view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [Oh, S. et
al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]. Auxiliary scans
for slice alignment and motion- and distortion-correction were performed at the
beginning of the first fMRI recording session and also after the break at the
start of the recording for the second half of the movie.

% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time (TR),
\unit[30]{ms} echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px}
bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction
factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order. Philips' ``SmartExam'' was
used to automatically position slices in AC-PC orientation such that the topmost
slice was located at the superior edge of the brain. This automatic slice
positioning procedure was identical in the AV und VIS study and yielded a
congruent geometry across paradigms.

% no. of volumes
A total of 3599 volumes were recorded for each participant in each of the
naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338 volumes for segment 1–8 respectively).

@@

\todo[inline]{bin wie immer bzgl. motion correction \& Templateerstellung unsicher}

\todo[inline]{motion correction \& Templateerstellung: cite sengupta2016 where this was first done and described, ie same
image/data was used here => dort finde ich nur links

https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code

https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}

\todo[inline]{Satz zum Downsampling der 7T Daten? => check github repo}

% data source
fMRI time series data were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data are already aligned to a subject-specific
\href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3
Tesla BOLD template} by a rigid body transformation in MCFLIRT
\citep{jenkinson2002registration} to correct for motion during scanning
\citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant was dropped to due to invalid distortion correction
during scanning of the AO stimulus

>>>>

% what we did data source
In this study, we analyze functional data of the same 14 participants provided
by the studyforrest dataset \href{http://www.studyforrest.org}{studyforrest.org}; \citep{hanke2014audiomovie, hanke2016simultaneous}).
% PPA + movie + audio-description
We annotated cuts in the movie ``Forrest Gump'', and words spoken by an
additional narrator in the movie's audio-description (i.e. the movie's
audio-only variant) to exploratorily investigate how the parahippocampal gyrus
behaves during lifelike stimulation.
% model-driven analysis
In conformity to the analyses performed in the reviewed studies,  we also
employed a standard multi-level, voxel-wise general linear model
(GLM).\todo{why? in order to\dots}
% focus on audio-description
Encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus
on the audio-description as a naturalistic, auditory-only paradigm free from any task to localize a ``visual area'' in individual study participants.
% comparison to dedicated localizer
Finally, we compare our results to results of a dedicated visual localizer
experiment done with the same 14 participants \citep{sengupta2016extension}.

@@

% intro
We used data from three publicly available datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) which have already been
used by other research groups for independent research questions.
% used studies
\todo{this is just loveless listing so far but it's 'complete'} The same
subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration},
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}, a dataset already used by
\citep{ben2018hippocampal},
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study) \citep{sengupta2016extension}, a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications \citep{hanke2014audiomovie, hanke2016simultaneous,
sengupta2016extension}. Following is a summary of most important aspects.

\subsection{Participants}
% AO study
In the AO study \citep{hanke2014audiomovie}, 20 German native speakers (all
right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest
Gump'' \citep{ForrestGumpMovie} as an additional audio track for visually
impaired listeners on Swiss public television.
% AV study
In the AV study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
mean age 29.4, six female) of the prior AO study watched the audio-visual movie
with dubbed German audio track \citep{ForrestGumpDVD}.
% VIS study
In the VIS study \citep{sengupta2016extension}, the same 15 participants took
part in a six-category block-design visual localizer.

% participants' health
All participants reported to have normal hearing, normal or corrected-to-normal
vision, and no known history of neurological disorders.
% compensation, consent and shit
In all studies, participants received monetary compensation and gave written
informed consent for their participation and for public sharing of obtained data
in anonymized form. The studies had prior approval by the Ethics Committee of
Otto-von-Guericke University of Magdeburg, Germany.

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned
audio-description (i.e. the audio-only variant of the movie) that was broadcast
as an additional audio track for visually impaired listeners on Swiss public
television \citep{ForrestGumpGermanAD}.
% AO vs. AV: differences
The plot of the movie is already carried by an off-screen voice-over of the main
character Forrest Gump. In the largely identical audio-description, an
additional male narrator describes essential aspects of the visual scenery when
there is no off-screen voice, dialog, or other relevant auditory content.

@@

% VIS study picture categories
All stimuli for the VIS study were used in a previous study
\citep{haxby2011common}. There were 24 unique greyscale images (matched in
luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
categories: human faces, human bodies without heads, small objects, houses and
outdoor scenes comprising of nature and street scenes, and phase scrambled
images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.

@@

% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted location \citep{haeusler2016cutanno}.
% AO anno
For the analysis of the AO data, we extended another publicly available
annotation of speech \citep{haeusler2020speechanno}. We manually annotated words
spoken by the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns embedded in sentences spoken by
the narrator to describe the movie's missing visual content. Some categories
were created in such a way to reflect the six stimulus categories used in the
visual localizer experiment. Some additional categories were created to
semantically cluster nouns into categories ``that were obvious to make
sense''.\todo{yeah, well, sounds shit but that's basically it}.
% categories Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der
% Zeit.
More specifically, nouns were categorized by the clue they provide about the
cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old),
its inherent persons (female, female name; male, male name, person), a person's
appearance (face, head; body, bodypart), and a scene's inherent objects (object,
furniture).
% reference to table
A complete overview of all categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules (see
Table. Minor corrections due to incorrectly applied rules were by the author (s.
Table \ref{tab:descr-nouns-counts} for the counts in the whole stimulus and the
eight stimulus segments used during fMRI scanning).

@@

% rules Tabelle für descriptiven nouns
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-description's narrator:
    cateogries, annotation rules and examples (given in English). The categorie
    \texttt{++} also contains adverbial adjectives and adverbs}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & moveable objects insides and outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundarie & telephone, car \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & recurring setting & at the ``bus stop'' \tabularnewline
++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

@@

% table of descriptive nouns counts
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-descriptions narrator:
        counts for the whole audio-only stimulus and its eight segments used
        during fMRI scanning.}
\label{tab:descr-nouns-counts}
\begin{tabular}{llllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
body & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline
bodypart &  \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline
face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline
female & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline
females & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline
fname & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline
furniture & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline
geo & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline
geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline
head & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline
male & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline
males & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline
mname & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline
object & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline
objects & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline
persons & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline

@@

\subsection{Procedure}
% questionnaire
In all three studies, participants filled out a questionnaire on their basic
demographic information and familiarity with the movie).
% AO & AV: instructions
Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

% VIS: presentation & instructions
In the VIS study, participants were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run, while they also
performed a one-back matching task to keep them attentive.

@@

% AV & VIS
In the AV and VIS study, visual instructions and stimuli were presented on a
rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with
EXT-DVI-FM1000)].
% screen size
The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p}
resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with
\unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$
21.2]{cm}.
% angle of view: AV
In the AV study, this corresponded to \unit[23.75 $\times$ 13.5] or \unit[23.75
$\times$ 10.25]{cm} when considering only the movie content and excluding the
horizontal gray bars.
% angle of view: VIS
In the VIS study, stimulus images were displayed at a size of approximately
\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.

\todo[inline]{auditory stimulation was the same in AO and AV?}

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices & FOV
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a 10 percent inter-slice gap were recorded in ascending order.
Slices were oriented to include the ventral the ventral portions of frontal and
occipital cortex while minimizing intersection with the eyeballs. The field of
view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [Oh, S. et
al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]. Auxiliary scans
for slice alignment and motion- and distortion-correction were performed at the
beginning of the first fMRI recording session and also after the break at the
start of the recording for the second half of the movie.

% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time (TR),
\unit[30]{ms} echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px}
bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction
factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order. Philips' ``SmartExam'' was
used to automatically position slices in AC-PC orientation such that the topmost
slice was located at the superior edge of the brain. This automatic slice
positioning procedure was identical in the AV and VIS study, and yielded a
congruent geometry across paradigms.

% no. of volumes
A total of 3599 volumes were recorded for each participant in each of the
naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338 volumes for segment 1–8).

@@

\todo[inline]{as usually I am pretty unsure about correct report of motion
correction \& template creation}
\todo[inline]{Satz zum Downsampling der 7T Daten? => check github repo}
% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
fMRI time series data were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data are already aligned to a subject-specific
\href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3
Tesla BOLD template} by a rigid body transformation in MCFLIRT
\citep{jenkinson2002registration} to correct for motion during scanning
\citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant was dropped to due to invalid distortion correction
during scanning of the AO stimulus
